Cover Letter

### 2017-12-26 paper/sections/6_results.tex
paper: wordsmithing
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application.  \newcomment{These techniques have already proven to be
effective and scalable in systems that specialize an entire namespace according
to a single optimization strategy (e.g., Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with/without isolation.}

\newcomment{\indent We run experiments on the same cluster and graph the
standard deviations for three runs (sometimes error bars are too small to see).
We also normalize results to control for hardware differences and to make our
results more generally applicable. We use a CloudLab cluster of 34 nodes
connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and SSDs.
Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel release, version
10.2.1, which was released in May 2016. All daemons run as a single process
(the default setting for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.} We scope the
evaluation to one metadata server and scale the number of parallel
clients\newcomment{ each doing 100K operations}\footnote{This is the maximum
recommended size of a directory in CephFS; preliminary experiments with larger
directory sizes show memory problems.}. This type of analysis shows the
capacity and performance of a metadata server with superior metadata protocols,
which should be used to inform load balancing across a metadata cluster. Load
balancing across a cluster of metadata servers with partitioning and
replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.

@@

\oldcomment{Figure~\ref{fig:composable-mechanisms} shows the runtime of the
Cudele mechanisms for a single client creating files in the same directory, }
\newcomment{We measure the overhead of each mechanism by having 1 client create
100K files in a directory for various subtree configurations.
Figure~\ref{fig:composable-mechanisms} shows the time that it takes each Cudele
mechanism to process all metadata events.  Results are} normalized to the time
it takes to write 100K file create updates to the client's in-memory journal
({\it i.e.} the Append Client Journal mechanism).  \newcomment{The first graph
groups the consistency mechanisms, the second groups the durability mechanisms,
and the third has compositions representing real-world systems.} Stream is an
approximation of the overhead and is calculated by subtracting the runtime of
the job with the journal turned off from the runtime with the journal turned
on.  \oldcomment{100K is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.}

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large
slowdowns\oldcomment{ for the larger number of creates}. For example, RPCs has
a \oldcomment{\(90\times\)}\newcomment{\(18\times\)} slowdown because this
technique relies on the internal directory data structures. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal experience a much less drastic slowdown because the journal
data structure does not need to be scanned for every operation.  Events are
written to the end of the journal without even checking the validity ({\it
e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} RPCs is
\oldcomment{\(66\times\)}\newcomment{\(19.9\times\)} slower than Volatile Apply
because sending individual metadata updates over the network is costly.  While
RPCs sends a request for every file create, Volatile Apply \oldcomment{writes
all the updates to the in-memory journal and applies them}\newcomment{writes
directly} to the in-memory data structures in the metadata server. While
communicating the decoupled namespace directly to the metadata server
\newcomment{with Volatile Apply} is faster, communicating through the object
store \newcomment{with Nonvolatile Apply} is
\oldcomment{\(10\times\)}\newcomment{\(78\times\)} slower.

% TODO: why is apply so slow.  apply: no CephFS changes, pulls/pushes same
% RADOS obj.  v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of Nonvolatile Apply:} The cost of Nonvolatile Apply is much
larger than all the other mechanisms.  That mechanism was not implemented as
part of Cudele -- it was a debugging and recovery tool packaged with CephFS. It
works by iterating over the updates in the journal and pulling all objects that
{\it may} be affected by the update.  This means that two objects are
repeatedly pulled, updated, and pushed: the object that houses the experiment
directory and the object that contains the root directory ({\it i.e.},
\texttt{/}).  The cost of communicating through the object store is shown by
comparing the runtime of Volatile Apply + Global Persist
\newcomment{(\(1.3\times\))} to Nonvolatile Apply\newcomment{ (\(78\times\))}.
These two operations end up with the same final metadata state but using
Nonvolatile Apply is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} \newcomment{Stream has the highest
slowdown at \(2.4\times\) because the overhead of maintaining and streaming the
journal is incurred by the metadata server}.  Comparing Local and Global
Persist demonstrates the bandwidth advantages of storing the journal in a
distributed object store. The Global Persist performance is \newcomment{only
\(0.2\times\) slower than Local Persist because Global
Persist}\oldcomment{\(1.5\times\) faster because the object store} is
leveraging the collective bandwidth of the disks in the cluster. This benefit
comes from the object store itself but should be acknowledged when making
decisions for the application; the bandwidth of the object store can help
mitigate the overheads of globally persisting metadata updates. The storage per
journal update is about 2.5KB. So the storage footprint scales linearly with
the number of metadata creates and suggests that updates for a million files
would be \newcomment{2.38GB}\oldcomment{2.5KB \(*\) 1 million files \(=\)
2.38GB. Transfer times for payloads of this size in most HPC/data center
networks are reasonable.}

@@

\newcomment{{\it Composing Mechanisms}: The graph on the right of
Figure~\ref{fig:composable-mechanisms} shows how applications can compose
mechanisms together to get the consistency/durability guarantees they need in a
global namespace.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  Again, the
runtime is normalized to creating files in the client's in-memory journal.  We
make no guarantees during execution of the mechanisms or when transitioning
semantics -- the semantics are guaranteed {\it once the mechanism completes}.
So if servers fail during a mechanism, metadata or data may be lost. This graph
shows how we can build application-specific subtrees by composing mechanisms
and that coupling well-established techniques to specific applications results
in a more scalable global namespace.}

\subsection{Use Case 1: Creates in the Same Directory}
\label{sec:use-case-1}

\oldcomment{Next we show how we can build application-specific subtrees by composing
mechanisms and that \oldcomment{this approach}\newcomment{coupling
well-established techniques to specific applications} results in a more a
scalable global namespace.  }

We start with clients creating files in private directories because this
workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
But the workload also appears in cloud workloads~\cite{xiao:socc15-shardfs},
where systems like Hadoop use the file abstraction to exchange work units to
workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}. \oldcomment{ The workload is clients creating 100K files
in private directories in the same global namespace. }

@@

\oldcomment{To show the contention at the metadata server, }In
Figure~\ref{fig:mergescale} we scale the number of clients \newcomment{each
doing 100K file creates in their own directories for three types of subtrees:
one with strong consistency and global durability (RPCs), one with invisible
consistency and local durability (decoupled: create), and one with weak
consistency and local durability (decoupled: create + merge). Results are
normalized to 1 client that creates 100K files using RPCs (about 549
creates/sec). As opposed to earlier graphs in
Section~\S\ref{sec:posix-overheads} that plotted the throughput of the slowest
client, Figure~\ref{fig:mergescale} plots the throughput from the perspective
of the metadata server. Plotting this way is easier to understand because of
how we normalize but the speedups over the RPC approach are the same, whether
we look at the slowest client or not.}

\newcomment{When the metadata server is operating at peak efficiency between 5
and 20 clients, ``decoupled: merge + create" outperforms ``RPCs" by
\(3.37\times\) because ``decoupled: merge + create" uses a relaxed form of
consistency and leverages bulk updates just liked
DeltaFS~\cite{zheng:pdsw2015-deltafs}.  The ``RPCs" and ``decoupled: merge +
create" curves flatten out at a slowdown of \(4.5\times\) and \(15\times\),
respectively, because more clients increases the load at the metadata server.
Alternatively, the ``decoupled: create" curve scales linearly with the number
of concurrent clients because clients operate in parallel and write updates
locally. At 20 clients, we observe a \(91.7\times\) speedup for ``decoupled:
create" over RPCs.}\oldcomment{ for the RPC per operation strategy and the
decoupled namespace strategy.  For RPCs, scaling the number of clients
increases the load on the metadata server and for decoupled we increase the
number of concurrent clients operating in parallel.  Related work has pointed
to on-disk metadata format as the primary factor for improved scalability; but
our results show that the weakened consistency and durability enables the
scalability improvements. The on-disk metadata formats in this experiment are
the same for all schemes.}

\newcomment{Another reason that} the performance of decoupled namespaces is
better than RPCs \newcomment{is because decoupled namespaces (1)} place no
restrictions on the validity of metadata inserted into the journal and
\newcomment{(2)} avoid touching poorly scaling data structures. We can scale
linearly if we weaken our consistency by never checking for the existence of
files before creating files ({\it i.e.} only append \texttt{open()} requests to
the journal).  When the updates are merged by the metadata server into the
in-memory metadata store they never scan growing data structures.  Had we
implemented the \oldcomment{Append Client Journal mechanism}\newcomment{client}
to include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen the poor scaling \newcomment{behavior} that we see with the RPCs
mechanism.

@@

\subsection{Use Case 2: Creates with Interfering Client}

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.
C}lients create 100K files in their own directories while another client interferes by
creating \oldcomment{more}\newcomment{1000} files in each directory. This
introduces false sharing and the metadata server revokes capabilities on
directories touched by the interfering client. While HPC tries to avoid these
situations with workflows~\cite{zheng:pdsw2014-batchfs,
zheng:pdsw2015-deltafs}, it still happens in distributed file systems when
users unintentionally access directories in a shared file system.
\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}

\newcomment{We switch back to clients doing RPCs per operation with journaling
enabled, to mirror the setup from the problem presented in
Figure~\ref{fig:overhead-b}.} Figure~\ref{fig:block-allow} plots the overhead
of the slowest client \oldcomment{and the error bars are the standard deviation
of 3 runs.  ``Interfere (Fig 3c)" is the result from
Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API to return
\texttt{-EBUSY} to interfering clients; and ``Isolated" is the baseline
performance without an interfering.  Each subtree has RPCs and Stream enabled.
Results are normalized to the runtime of a single client creating files in a
directory.  Note that IndexFS has a similar behavior to ``interfere" with
leases, except clients block.  }\newcomment{normalized to 1 client that creates
100K files in isolation (about 513 creates/sec). ``Interference" and ``no
interference" is the performance with and without an interfering client
touching files in every directory, respectively. The goal is to explicitly
isolate clients so that performance is similar to the ``no interfere" curve,
which has lower slowdowns (on average, \(1.42\times\) per client compared to
\(1.67\times\) per client for ``interfere") and less variability (on average, a
standard deviation of 0.06 compared to 0.44 for ``interfere").  ``Block
interference" uses the Cudele API to block interfering clients with
\texttt{-EBUSY}. That curve shows slowdowns similar to ``interfere" for smaller
clusters because the overhead to reject requests is more evident when the
metadata server is underloaded; but the slowdown (\(1.34\times\) per client)
and variability (0.09) look very similar to ``no interfere" for larger
clusters. Clients can block interfering clients to get the same performance as
isolated clients but there is a non-negligible overhead for rejecting requests
when the metadata server is not operating at peak efficiency.}

\oldcomment{We draw three conclusions: (1) clients that use the API to block interfering
clients  get the same performance as isolated clients, (2) there is a
negligible effect on performance for the extra work the metadata server does to
return \texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
negligible effect on performance.}

\oldcomment{\textbf{Takeaway}: the API lets users isolate directories when applications
need better and more reliable performance. Blocking updates is an effective way of
controlling consistency.}

\subsection{Use Case 3: Read while Writing}

The final use case shows how the API gives users fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Hadoop writes to temporary files,
renames them when complete, and creates a ``DONE" file to indicate to the
runtime that the task did not fail and should not be re-scheduled on another
node. In this scenario, Cudele users will not see the progress of decoupled
namespaces since their updates are not globally visible.  To help users judge
the progress of their jobs, Cudele clients have a ``namespace sync" that sends
batches of updates back to the global namespace at regular intervals.

% Does this implementation need to be described in the implementation?
\newcomment{We configure a subtree as a decoupled namespace with invisible
consistency, local durability, and partial updates enabled.}
Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to the decoupled namespace and
pausing to send updates to the metadata server. \oldcomment{The error bars are
the standard deviations of 3 runs.} We scale the namespace sync interval to
show the trade-off of frequently pausing or writing large logs of updates.  We
use an idle core to log the updates and to do the network transfer. The client
only pauses to fork off a background process, which is expensive as the address
space needs to be copied. The alternative is to pause the client completely and
write the update to disk but since this implementation is limited by the speed
of the disk, we choose the memory-to-memory copy of the fork approach.

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead), because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a 678MB journal.

>>>>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace\oldcomment{, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application}. \newcomment{These techniques have already proven to be
effective and scalable in systems that specialize an entire namespace according
to a single optimization strategy ({\it e.g.}, Lustre, BatchFS, DeltaFS), so our
evaluation explores the behavior of the consistency/durability mechanisms and
their effect with and without isolation.}

\newcomment{\indent We run experiments on the same cluster and graph the
standard deviations for three runs (sometimes error bars are too small to see).
We also normalize results to control for hardware differences and to make our
results more generally applicable. We use a CloudLab cluster of 34 nodes
connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and 400GB
SSDs.  Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel release,
version 10.2.1, which was released in May 2016. All daemons run as a single
process (the default setting for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 20 clients.} We scope the
evaluation to one metadata server and scale the number of parallel clients
\newcomment{each doing 100K operations}\footnote{This is the maximum
recommended size of a directory in CephFS; preliminary experiments with larger
directory sizes show memory problems.} \newcomment{We scale to 20 clients
because, as shown in Section~\S\ref{sec:posix-overheads}, 20 clients is enough
to saturate the resources of a single metadata server.} This type of analysis
shows the capacity and performance of a metadata server with superior metadata
protocols, which should be used to inform \oldcomment{load
balancing}\newcomment{metadata distribution} across a \oldcomment{metadata}
cluster. Load balancing across a cluster of metadata servers with partitioning
and replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.

@@

\oldcomment{Figure~\ref{fig:composable-mechanisms} shows the runtime of the
Cudele mechanisms for a single client creating files in the same directory, }
\newcomment{We measure the overhead of each Cudele mechanism by having 1 client create
100K files in a directory for various subtree configurations.
Figure~\ref{fig:composable-mechanisms} shows the time that it takes each Cudele
mechanism to process all metadata events.  Results are} normalized to the time
it takes to write \oldcomment{100K file create} updates to the client's in-memory journal
({\it i.e.} the Append Client Journal mechanism).  \newcomment{The first graph
groups the consistency mechanisms, the second groups the durability mechanisms,
and the third has compositions representing real-world systems.} \oldcomment{Stream is an
approximation of the overhead and is calculated by subtracting the runtime of
the job with the journal turned off from the runtime with the journal turned
on.  100K is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.}

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large
slowdowns\oldcomment{ for the larger number of creates}. For example, RPCs has
a \oldcomment{\(90\times\)}\newcomment{\(17.9\times\)} slowdown because this
technique relies on internal directory data structures\newcomment{, which is a
well-known problem~\cite{ren:sc2014-indexfs}}. \oldcomment{It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns.} Other mechanisms that write
events to a journal experience a much less drastic slowdown because the journal
data structure does not need to be scanned for every operation.  Events are
written to the end of the journal without even checking the validity ({\it
e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS TODO: why is apply so
% slow.  apply: no CephFS changes, pulls/pushes same RADOS obj.  v_apply vs.
% apply/persist: communicating through RADOS
{\it Overhead of \oldcomment{RPCs}\newcomment{Consistency}:} RPCs is
\oldcomment{\(66\times\)}\newcomment{\(19.9\times\)} slower than Volatile Apply
because sending individual metadata updates over the network is costly.  While
RPCs sends a request for every file create, Volatile Apply \oldcomment{writes
all the updates to the in-memory journal and applies them}\newcomment{writes
directly} to the in-memory data structures in the metadata server. While
communicating the decoupled namespace directly to the metadata server
\newcomment{with Volatile Apply} is faster, communicating through the object
store \newcomment{with Nonvolatile Apply} is
\oldcomment{\(10\times\)}\newcomment{\(78\times\)} slower.  \oldcomment{{\it
Overhead of Nonvolatile Apply:} The cost of Nonvolatile Apply is much larger
than all the other mechanisms.  That mechanism}\newcomment{Nonvolatile Apply}
was not implemented as part of Cudele -- it was a debugging and recovery tool
packaged with CephFS. It works by iterating over the updates in the journal and
pulling all objects that {\it may} be affected by the update.  This means that
two objects are repeatedly pulled, updated, and pushed: the object that houses
the experiment directory and the object that contains the root directory ({\it
i.e.}, \texttt{/}).  \oldcomment{The cost of communicating through the object
store is shown by comparing the runtime of Volatile Apply + Global Persist to
Nonvolatile Apply.  These two operations} \newcomment{Nonvolatile Apply
(\(78\times\)) and composing Volatile Apply + Global Persist (\(1.3\times\))}
end up with the same final metadata state but using Nonvolatile Apply is
clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} \newcomment{ Stream\footnote{This
measurement is an approximation of the overhead and is calculated by
subtracting the runtime of the job with the journal turned off from the runtime
with the journal turned on.} has the highest slowdown at \(2.4\times\)
because the overhead of maintaining and streaming the journal is incurred by
the metadata server}.  Comparing Local and Global Persist demonstrates the
bandwidth advantages of storing the journal in a distributed object store. The
Global Persist performance is \newcomment{only \(0.2\times\) slower than Local
Persist because Global Persist}\oldcomment{\(1.5\times\) faster because the
object store} is leveraging the collective bandwidth of the disks in the
cluster. This benefit comes from the object store itself but should be
acknowledged when making decisions for the application; the bandwidth of the
object store can help mitigate the overheads of globally persisting metadata
updates. The storage per journal update is about 2.5KB. So the storage
footprint scales linearly with the number of metadata creates and suggests that
updates for a million updates in a single journal would be
\newcomment{2.38GB}\oldcomment{2.5KB \(*\) 1 million files \(=\) 2.38GB.
Transfer times for payloads of this size in most HPC/data center networks are
reasonable.}

@@

\newcomment{{\it Composing Mechanisms}: The graph on the right of
Figure~\ref{fig:composable-mechanisms} shows how applications can compose
mechanisms together to get the consistency/durability guarantees they need in a
global namespace.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  We make no
guarantees during execution of the mechanisms or when transitioning semantics
-- the semantics are guaranteed {\it once the mechanism completes}.  So if
servers fail during a mechanism, metadata or data may be lost. This graph shows
how we can build application-specific subtrees by composing mechanisms and that
coupling well-established techniques to specific applications results in a more
scalable global namespace.}

\subsection{Use Cases}

\newcomment{Next we present three uses cases: creates in the same directory,
interfering clients, and read while writing. For each use case, we provide
motivation from HPC and cloud workloads; specifically, we look at users using
the file system in parallel to run large-scale experiments in HPC and parallel
runtimes that use the file system, such as Hadoop and Spark. The synthetic
benchmarks model scenarios where these workloads co-exist in a global namespace
and we provide insight into how the workload benefits from Cudele.}

\subsubsection{Creates in the Same Directory}
\label{sec:use-case-1}

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark, shvachko:login2012-hdfs-scalability}; Spark queries have an
O(\(n\)) complexity, where \(n\) is the number of partitions.  Big Data
Benchmark jobs examined in~\cite{chaimov:hpdc16-spark} have on the order of
15,000 file opens or creates just to start a single Spark query and the Lustre
system they tested on did not handle creates well, showing up to a \(24\times\)
slowdown compared to other metadata operations. Common approaches to solve
these types of bottlenecks is to change the application behavior or to design a
new file system, like BatchFS or DeltaFS, that uses one set of metadata
optimizations for the entire namespace.} \oldcomment{ abstraction to exchange
work units to workers or to indicate when jobs complete  The workload is
clients creating 100K files in private directories in the same global
namespace.}

\newcomment{\textbf{Cudele setup}: accommodate these workloads in the global
namespace by configuring three subtrees with the following semantics: one with
strong consistency and global durability (RPCs), one with invisible consistency
and local durability (decoupled: create), and one with weak consistency and
local durability (decoupled: create + merge).}

@@

\oldcomment{To show the contention at the metadata server, }In
Figure~\ref{fig:mergescale} we scale the number of clients \newcomment{each
doing 100K file creates in their own directories.  Results are normalized to 1
client that creates 100K files using RPCs (about 549 creates/sec). As opposed
to earlier graphs in Section~\S\ref{sec:posix-overheads} that plotted the
throughput of the slowest client, Figure~\ref{fig:mergescale} plots the
throughput of the total job ({\it i.e.} from the perspective of the metadata
server). Plotting this way is easier to understand because of how we normalize
but the speedups over the RPC approach are the same, whether we look at the
slowest client or not.}

\newcomment{When the metadata server is operating at peak efficiency at
20 clients, the performance of the ``RPCs" and ``decoupled: merge + create"
subtrees is bottlenecked by the metadata server processing power, so the curves
flatten out at a slowdown of \(4.5\times\) and \(15\times\), respectively.  On
the other hand, the ``decoupled: create" subtree performance scales linearly
with the number of concurrent clients because clients operate in parallel and
write updates locally. At 20 clients, we observe a \(91.7\times\) speedup for
``decoupled: create" over RPCs.}\oldcomment{ for the RPC per operation strategy
and the decoupled namespace strategy.  For RPCs, scaling the number of clients
increases the load on the metadata server and for decoupled we increase the
number of concurrent clients operating in parallel.  Related work has pointed
to on-disk metadata format as the primary factor for improved scalability; but
our results show that the weakened consistency and durability enables the
scalability improvements. The on-disk metadata formats in this experiment are
the same for all schemes.}

\newcomment{ ``Decoupled: merge + create" outperforms ``RPCs" by \(3.37\times\)
because ``decoupled: merge + create" uses a relaxed form of consistency and
leverages bulk updates just like DeltaFS~\cite{zheng:pdsw2015-deltafs}.
Decoupled namespaces (1)} place no restrictions on the validity of
metadata inserted into the journal ({\it e.g.}, never checking for the
existence of files before creating files), \newcomment{(2)} avoid touching
poorly scaling data structures\newcomment{, and (3) allow clients to batch
events into bulk updates}. \oldcomment{We can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files
({\it i.e.} only append \texttt{open()} requests to the journal).  When the
updates are merged by the metadata server into the in-memory metadata store
they never scan growing data structures.}  Had we implemented the
\oldcomment{Append Client Journal mechanism}\newcomment{client to send
updates one at a time and} to include \texttt{lookup()} commands before
\texttt{open()} requests, we would have seen \newcomment{performance closer to
the ``RPC" subtree}\oldcomment{the poor scaling that we see with the RPCs
mechanism}.

@@

\subsubsection{Interfering Clients}

Next we show how Cudele can be programmed to block interfering
clients\oldcomment{ using the same problematic workload from
Figure~\ref{fig:overhead-b}. In this workload, c}\newcomment{, which lets
applications control isolation to get better and more reliable performance.}
Clients create 100K files in their own directories while another client
interferes by creating \oldcomment{more}\newcomment{1000} files in each
directory. \oldcomment{This}\newcomment{The workload} introduces false sharing
and the metadata server revokes capabilities on directories touched by the
interfering client. While HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  \newcomment{ In the cloud, Spark and
Hadoop stacks use HDFS, which lets users ignore this type of consistency completely
by letting interfering clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}.}

\newcomment{\textbf{Cudele setup}: enable global durability with Stream and
strong consistency with RPCs to mirror the setup from the problem presented in
Figure~\ref{fig:overhead-b}. We configure one subtree with an interfere policy
of ``allow" and another with subtree with ``block" so \texttt{-EBUSY} is
returned to interfering clients.  The former is the default behavior in file
systems and the latter isolates performance from malicious clients.}

\oldcomment{We only scale to 15 clients because the performance variability of
a nearly overloaded metadata server, in our case 18 clients, is too high.}
Figure~\ref{fig:block-allow} plots the overhead of the slowest
client\oldcomment{and the error bars are the standard deviation of 3 runs.
``Interfere (Fig 3c)" is the result from Figure~\ref{fig:overhead-b};
``Interfere" uses the allow/block API to return \texttt{-EBUSY} to interfering
clients; and ``Isolated" is the baseline performance without an interfering.
Each subtree has RPCs and Stream enabled.  Results are normalized to the
runtime of a single client creating files in a directory.  Note that IndexFS
has a similar behavior to ``interfere" with leases, except clients block.
}\newcomment{, normalized to 1 client that creates 100K files in isolation
(about 513 creates/sec). ``Interference" and ``no interference" is the
performance with and without an interfering client touching files in every
directory, respectively. The goal is to explicitly isolate clients so that
performance is similar to the ``no interfere" curve, which has lower slowdowns
(on average, \(1.42\times\) per client compared to \(1.67\times\) per client
for ``interfere") and less variability (on average, a standard deviation of
0.06 compared to 0.44 for ``interfere").  ``Block interference" uses the Cudele
API to block interfering clients and the slowdown (\(1.34\times\) per client)
and variability (0.09) look very similar to ``no interfere" for larger
clusters. For smaller clusters the overhead to reject requests is more evident
when the metadata server is underloaded so the slowdowns are similar to
``interfere".  Clients can block interfering clients to get the same
performance as isolated clients but there is a non-negligible overhead for
rejecting requests when the metadata server is not operating at peak
efficiency.}

\oldcomment{We draw three conclusions: (1) clients that use the API to block
interfering clients  get the same performance as isolated clients, (2) there is
a negligible effect on performance for the extra work the metadata server does
to return \texttt{-EBUSY}, and (3) merging updates from the decoupled client
has a negligible effect on performance.  \textbf{Takeaway}: the API lets users
isolate directories when applications need better and more reliable
performance. Blocking updates is an effective way of controlling consistency.}

\subsubsection{Read while Writing}

The final use case shows how the API gives users fine-grained control of the
consistency semantics \newcomment{to support current practices and experimental
workflows}. \oldcomment{The use case is that u}\newcomment{U}sers often
leverage the file system to check the progress of jobs using \texttt{ls} even
though this operation is notoriously heavy-weight~\cite{carns:ipdps09-pvfs,
eshel:fast10-panache}. The number of files or size of the files is indicative
of the progress. This practice is not too different from systems that use the
file system to manage the progress of jobs; Spark and Hadoop write to temporary
files, renames them when complete, and creates a ``DONE" file to indicate to
the runtime that the task did not fail and should not be re-scheduled on
another node. \newcomment{Also, the browser interface lets users check the
progress by querying the file system and returning a \% of job complete
metric.}

% Does this implementation need to be described in the implementation?
\newcomment{\textbf{Cudele setup}: in this scenario, Cudele users will not see
the progress of decoupled namespaces since their updates are not globally
visible.  To provide the performance of decoupled namespaces and to help users
judge the progress of their jobs, Cudele clients have a ``namespace sync" that
sends batches of updates back to the global namespace at regular intervals.
We configure a subtree as a decoupled namespace with invisible consistency, local
durability, and partial updates enabled.}

Figure~\ref{fig:slowdown-sync} shows the performance degradation of a single
client writing \newcomment{1 million} updates to the decoupled namespace and
pausing to send updates to the metadata server. \oldcomment{The error bars are
the standard deviations of 3 runs.} We scale the namespace sync interval to
show the trade-off of frequently pausing or writing large logs of updates.  We
use an idle core to log the updates and to do the network transfer. The client
only pauses to fork off a background process, which is expensive as the address
space needs to be copied. The alternative is to pause the client completely and
write the update to disk but since this implementation is limited by the speed
of the disk, we choose the memory-to-memory copy of the fork approach.

As expected, syncing namespace updates too frequently has the highest overhead
(up to 9\% overhead if done every second). The optimal sync interval for
performance is 10 seconds, which only incurs 2\% overhead), because larger
intervals must write more updates to disk and network. For the 25 second
interval, the client only pauses 3-4 times but each sync writes about 278
thousand updates at once, which is a journal of size 678MB.
